%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

\begin{cventries}
%---------------------------------------------------------
\cventry
    {Full-stack SWE1 with back-end focus | Java, Spring, React, JavaScript, AWS} % Job title
    {PowerAdvocate} % Organization
    {Boston MA} % Location
    {May 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Contributed to redesign of a monolithic web application into a microservice-oriented architecture and monetizable API (siqs).}
        \item {Developed NodeJS microservice allowing analysts to search by using Elasticsearch, increasing searching accuracy.}
        \item {Practiced Agile Development under a Continuous Flow framework, collaborating with other developers by pair programming.}
        \item {Created unit and integration tests using Jest to ensure reliability and resiliency of software.}
      \end{cvitems}
    }
%---------------------------------------------------------
\cventry
    {Full Stack Software Development Co-op | React, JavaScript, Java, Elasticsearch, AWS} % Job title
    {PowerAdvocate} % Organization
    {Boston MA} % Location
    {July 2019 - Dec. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Contributed to redesign of a monolithic web application into a microservice-oriented architecture and monetizable API (siqs).}
        \item {Developed NodeJS microservice allowing analysts to search by using Elasticsearch, increasing searching accuracy.}
        \item {Practiced Agile Development under a Continuous Flow framework, collaborating with other developers by pair programming.}
        \item {Created unit and integration tests using Jest to ensure reliability and resiliency of software.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Undergraduate Researcher | Python, C++, OpenCV, ROS} % Job title
    {Northeastern University RIVeR Laboratory} % Organization
    {Boston MA} % Location
    {Jan. 2018 - July 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed facial recognition and person following packages for the Toyota HSR in a RoboCup@Home competition.}
        \item {Placed 4$^{th}$ internationally in a RoboCup@Home competition in Montreal, Canada as part of a team of 6 researchers.}
        \item {Researched, built, and tested a prototype autonomous navigation system based on optical flow.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Advanced Concepts Co-op | Java, ANSYS} % Job title
    {Draper Laboratory} % Organization
    {Cambridge MA} % Location
    {Jan. 2017 - July 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created a Java application to translate system engineering models between OpenMETA and sysML.}
        \item {Modernized existing file system approach by utilizing a graph database as a single source of truth for system engineering models.}
        \item {Integrated database and Java app into continuous integration workflow for engineering models, greatly improving efficiency.}
        \item {Utilized ANSYS Electronic Desktop to model operational effects of varying RF wavelengths on a PCB based on trace dimensions.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
