%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Technical Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
    \cventry
    {Distributed Systems, Data Analytics | Rust} % Project type
    {LiquidML} % Project name
    {Boston MA} % Location
    {February 2020 - Aoril 2020} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Designed and implemented a well-documented crate (docs.rs/liquid-ml) for a distributed, horizontally scalable platform for data analysis on data sets too large to fit into memory. Created an API which allows users to implement User-Defined Functions.}
        \item {Implemented decision tree and random forest machine learning algorithms on the platform}
      \end{cvitems}
    }

    \cventry
    {File parsing | Rust} % Project type
    {Sorer} % Project name
    {Boston MA} % Location
    {Jan. 2020 - Feb. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Designed and built a high performance, multi-threaded CSV file parser. Infers schema on read based on a probabilistic algorithm.}
        \item {Documented (docs.rs/sorer) and published the project with an idiomatic structure and API to crates.io}
        \item {Analyzed performance under various circumstances using perf and flamegraphs}
      \end{cvitems}
    }

    \cventry
    {System shell | Rust} % Project type
    {gshell} % Project name
    {Boston MA} % Location
    {Sep. 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Implemented a system shell for Unix Platforms using a custom lexer and parser to construct ASTs from user input according to operator precedence. Supports common bash syntax and operators such as pipes, redirects, boolean logic, etc.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Web Development | React, JavaScript, HTML, CSS, Gatsby} % Project type
    {Personal Website} % Project name
    {Boston MA} % Location
    {July 2019} % Date(s)
    {
      \begin{cvitems} % Description(s)
        \item {Designed and developed a responsive website to display personal projects and a professional resume.}
      \end{cvitems}
    }
    

\end{cventries}
